Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Updated Figure 6 (still need to work on that)

error_df_scurve <- error_df_scurve |>
  mutate(type = case_when(
    row_wise_abs_error == 0 ~ "no error",
    row_wise_abs_error <= 0.2 ~ "error 0-0.2",
    row_wise_abs_error <= 0.4 ~ "error 0.2-0.4",
    row_wise_abs_error <= 0.6 ~ "error 0.4-0.6",
    .default = "error greter than 0.6"
  )) |>
  mutate(type = factor(type, levels = c(
    "no error", "error 0-0.2", "error 0.2-0.4", "error 0.4-0.6", "error greter than 0.6")))

@@

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  scale_colour_brewer(
    type = "qual",
    palette = 2
  ) +
  theme(
    legend.position = "right",
    legend.text = element_text(size = 10)
  ) +
  coord_equal()
```

>>>>

# error_df_scurve <- error_df_scurve |>
#   mutate(type = case_when(
#     row_wise_abs_error == 0 ~ "no error",
#     row_wise_abs_error <= 0.2 ~ "error 0-0.2",
#     row_wise_abs_error <= 0.4 ~ "error 0.2-0.4",
#     row_wise_abs_error <= 0.6 ~ "error 0.4-0.6",
#     .default = "error greter than 0.6"
#   )) |>
#   mutate(type = factor(type, levels = c(
#     "no error", "error 0-0.2", "error 0.2-0.4", "error 0.4-0.6", "error greter than 0.6")))

error_df_scurve <- error_df_scurve |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

@@

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  coord_equal()
```
